Experience Report: Haskell in Computational Biology

### 2012-07-02 mrfy_experience_report.tex
fix reference
rewrite of profiling para

GHC's profiler assigns costs not to functions but to ``cost
centers'' \cite{sansom-pj}.
In GHC~7.0, which we used 
for most of MRFy's development, 
cost-center annotations can be added automatically only
to top-level 
functions.
But most of our code is in nested functions.
We~annotated such functions manually,
but the annotations
made our code so ugly that we felt compelled to
remove them as soon as possible.
Without the annotations, however, GHC's call-site and allocation
profiles did not give us enough information to be useful.
We~miss valgrind, whose profiler gives useful information
without \emph{any} annotations.
GHC~7.4 provides much
better profiling tools, which eliminate most of these obstacles,
rendering this experience no longer as relevant.
\remark{given that this experience is no longers as relevant,
and we're tight on space, should we cut this entire paragraph
about profiling? --ND}

@@

\bibitem[Daniels et~al.(2012)Daniels, Hosur, Berger, and Cowen]{Daniels:2012}
Noah Daniels, Raghavendra Hosur, Bonnie Berger, and Lenore Cowen.
\newblock {SMURFLite: combining simplified Markov random fields with simulated
  evolution improves remote homology detection for beta-structural proteins
  into the twilight zone}.
\newblock \emph{Bioinformatics (to appear)}, 2012.

>>>>

GHC's profiler assigns costs not to functions but to ``cost
centers'' \cite{sansom-pj}.
In GHC~7.0, which we used 
for most of MRFy's development, 
cost-center annotations must be added manually
to nested functions.
The annotations
made our code so ugly that we felt compelled to
remove them as soon as possible.
Nonetheless, GHC's profiler led us to the performance
improvements discussed in \secref{perf}.
We~miss valgrind, whose profiler gives useful information
without \emph{any} annotations.
GHC~7.4 provides much
better profiling tools, which eliminate most of these obstacles,
and we look forward to further profiling MRFy.

@@

\bibitem[Daniels et~al.(2012)Daniels, Hosur, Berger, and Cowen]{Daniels:2012}
Noah Daniels, Raghavendra Hosur, Bonnie Berger, and Lenore Cowen.
\newblock {SMURFLite: combining simplified Markov random fields with simulated
  evolution improves remote homology detection for beta-structural proteins
  into the twilight zone}.
\newblock \emph{Bioinformatics}, March 2012.
